---
title: "finntools: finnhub.io made fast"
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
options(scipen = 999999)
```

# finntools

Finnhub.io offers a wide range of financial data at a price that the average investor can afford. However, much of this information is more useful to users in table format, rather than json. `finntools` helps shorten the gap between data retrieval and usage in a way that provides instant results for beginners and flexibility for more advanced users. Functions will be updated over time. Current ones retrieve:

#### company-based functions
* `get_company_news` news about a company within a given time period
* `get_sentiments` sentimental analyses of recent articles about a company
* `get_basic_financials` basic financial information about a company
* `get_reported_financials` financial information reported by a company through filings
* `get_company_filings` filings by a company
* `get_recommendation_trends` recommendation trends for a given company
* `get_company_peers` stocks with the same country and GICS sub-industry as the specified company
* `get_target_price` the latest price target consensus for a given company
* `get_earnings_surprise` company historical quarterly earnings surprise dating back to 2000
* `get_stock_candles` candlestick data for U.S. stocks dating as far back as 25 years
* `get_pattern_recognition` results of a pattern recognition algorithm on a given stock
* `get_quote` real-time data for a given stock
* `get_stock_splits` stock splits for a given symbol
* `get_support_resistance` support and resistance levels for a given company
* `get_aggregate_indicators` aggregate signal of multiple technical indicators (e.g. MACD, RSI, MA)
* `get_technical_indicators` technical indicator data for a given symbol

#### market-based functions
* `get_market_news` latest articles for overall market
* `get_ipo_calendar` ipo calendar for overall market

## Installation

```{r, eval = FALSE}
### Install from Github
require(devtools)
devtools::install_github('atamalu/finntools')
```

```{r, warning = FALSE, message = FALSE}
library(finntools)
```

## Functions

### get_company_news

`get_company_news` retrieves news about a company for a given time range

#### Example

Let's say we want to get the last 30 days of news for Apple

```{r, eval = FALSE, echo = TRUE}
get_company_news(symbol = 'AAPL', 
                 api.key = api.key,
                 last.n.days = 30)
```
```{r, eval = TRUE, echo = FALSE}
get_company_news(symbol = 'AAPL', 
                 api.key = api.key,
                 last.n.days = 30) %>%
  head() %>%
  kable()
Sys.sleep(3)
```

Or we may want to get news for Apple from March of 2020

```{r, eval = FALSE, echo = TRUE}
get_company_news(symbol = 'AAPL', 
                 api.key = api.key,
                 start.date = '2020-03-01', 
                 end.date = '2020-03-30')
```
```{r, eval = TRUE, echo = FALSE}
get_company_news(symbol = 'AAPL', 
                 api.key = api.key,
                 start.date = '2020-03-01', 
                 end.date = '2020-03-30') %>%
  head() %>%
  kable()
Sys.sleep(3)
```

Note: the API limits the number of results, which could be an issue for larger companies.

### get_sentiments

`get_sentiments` retrieves sentiment analyses of recent articles for a given company

#### Example

If we wanted to get sentiment analyses for Apple, we would use

```{r, eval = FALSE, echo = TRUE}
get_sentiments(symbol = "AAPL",
               api.key = api.key)
```
```{r, eval = TRUE, echo = FALSE}
get_sentiments(symbol = "AAPL",
               api.key = api.key) %>%
  head() %>%
  kable()
Sys.sleep(3)
```

### get_basic_financials

`get_basic_financials` retrieves basic financial information for a given company

#### Example

To get basic financial price data for Apple, we would enter:

```{r, eval = FALSE, echo = TRUE}
get_basic_financials(symbol = "AAPL", 
                     api.key = api.key, 
                     metric.type = "price")
```
```{r, eval = TRUE, echo = FALSE}
get_basic_financials(symbol = "AAPL", 
                     api.key = api.key, 
                     metric.type = "price") %>%
  head() %>%
  kable()
Sys.sleep(3)
```

### get_reported_financials

`get_reported_financials` retrieves financial data through a company's filings

#### Example

To get annual reported financial data for Apple, we would enter:

```{r, eval = FALSE, echo = TRUE}
get_reported_financials(symbol = "AAPL", 
                     api.key = api.key, 
                     frequency = "annual")
```
```{r, eval = TRUE, echo = FALSE}
get_reported_financials(symbol = "AAPL", 
                     api.key = api.key, 
                     frequency = "annual") %>%
  head() %>%
  kable()
Sys.sleep(3)
```

### get_company_filings

`get_company_filings` retrieves filings for a specified company or identifier

#### Example

If we wanted filings for Apple between the beginning of January 2020 and the end of March 2020, we'd do

```{r, eval = FALSE, echo = TRUE}
get_company_filings(symbol = "AAPL", 
                    api.key = api.key,
                    start.date = '2020-01-01', 
                    end.date = '2020-03-31')
```
```{r, eval = TRUE, echo = FALSE}
get_company_filings(symbol = "AAPL", 
                    api.key = api.key,
                    start.date = '2020-01-01', 
                    end.date = '2020-03-31') %>%
  head() %>%
  kable()
Sys.sleep(3)
```

### get_recommendation_trends

`get_recommendation_trends` retrieves recommendation trends for a given company

#### Example

If we wanted recommendation trends for Apple, we'd type

```{r, eval = FALSE, echo = TRUE}
get_recommendation_trends(symbol = "AAPL", 
                          api.key = api.key)
```
```{r, eval = TRUE, echo = FALSE}
get_recommendation_trends(symbol = "AAPL", 
                          api.key = api.key) %>%
  head() %>%
  kable()
Sys.sleep(3)
```

### get_company_peers

`get_company_peers` retrieves a data frame of stocks with the same country and GICS sub-industry as the specified symbol

#### Example

If we wanted to find companies that are similar to Apple, we'd use

```{r, eval = FALSE, echo = TRUE}
get_company_peers(symbol = "AAPL", 
                  api.key = api.key)
```
```{r, eval = TRUE, echo = FALSE}
get_company_peers(symbol = "AAPL", 
                  api.key = api.key) %>%
  head() %>%
  kable()
Sys.sleep(3)
```

### get_target_price

`get_target_price` retrieves the latest price target consensus for a given stock symbol

#### Example

Let's say that we want to get target prices for Apple

```{r, eval = FALSE, echo = TRUE}
get_target_price(symbol = 'AAPL',
                 api.key = api.key)
```
```{r, eval = TRUE, echo = FALSE}
get_target_price(symbol = 'AAPL',
                 api.key = api.key) %>%
  head() %>%
  kable()
Sys.sleep(3)
```

### get_earnings_surprise

`get_earnings_surprise` retrieves company historical quarterly earnings surprise dating back to 2000

#### Example

Let's say that we want to get earnings surprises for Apple from the 4 most recent periods

```{r, eval = FALSE, echo = TRUE}
get_earnings_surprise(symbol = 'AAPL', 
                      num.periods = 4, 
                      api.key = api.key)
```
```{r, eval = TRUE, echo = FALSE}
get_earnings_surprise(symbol = 'AAPL', 
                      num.periods = 4, 
                      api.key = api.key) %>%
  head() %>%
  kable()
Sys.sleep(3)
```

### get_market_news

`get_market_news` retrieves latest news for a market in a given category

#### Example

To get the latest market news on mergers, we'd enter

```{r, eval = FALSE, echo = TRUE}
get_market_news(category = "merger",
                api.key = api.key)
```
```{r, eval = TRUE, echo = FALSE}
get_market_news(category = "merger",
                api.key = api.key) %>%
  head() %>%
  .[1,] %>% # only return 1 row to fit table to github page
  kable()
Sys.sleep(3)
```

### get_ipo_calendar

`get_ipo_calendar` retrieves information on ipo's for a given time period

#### Example

Let's say we want to get ipo's from the last 30 days

```{r, eval = FALSE, echo = TRUE}
get_ipo_calendar(api.key = api.key, 
                 last.n.days = 30)
```
```{r, eval = TRUE, echo = FALSE}
get_ipo_calendar(api.key = api.key, 
                 last.n.days = 30) %>%
  head() %>%
  kable()
Sys.sleep(3)
```

Or we may want to get information on ipo's from March of 2020

```{r, eval = FALSE, echo = TRUE}
get_ipo_calendar(api.key = api.key, 
                 start.date = '2020-03-01', 
                 end.date = '2020-03-31')
```
```{r, eval = TRUE, echo = FALSE}
get_ipo_calendar(api.key = api.key, 
                 start.date = '2020-03-01', 
                 end.date = '2020-03-31') %>%
  head() %>%
  kable()
Sys.sleep(3)
```

### get_stock_candles

`get_stock_candles` retrieves candlestick data for U.S. stocks dating as far back as 25 years

#### Example

If we wanted stock candles for Apple from the 5 hours in 1-minute intervals, we'd enter

```{r, eval = FALSE, echo = TRUE}
to.date <- as.numeric(.POSIXct(Sys.time()))
from.date <- to.date - (5*3600)

get_stock_candles(symbol = 'AAPL', 
                  api.key = api.key,
                  resolution = 1,
                  from.date = from.date, 
                  to.date = to.date)
```
```{r, eval = TRUE, echo = FALSE}
to.date <- as.numeric(.POSIXct(Sys.time()))
from.date <- to.date - (5*3600)

get_stock_candles(symbol = 'AAPL', 
                  api.key = api.key,
                  resolution = 1,
                  from.date = from.date, 
                  to.date = to.date) %>%
  head() %>%
  kable()
Sys.sleep(3)
```

### get_pattern_recognition

`get_pattern_recognition` runs a pattern recognition algorithm on a given stock

#### Example

To run a pattern recognition algorithm for Apple with resolution of 1 day

```{r, eval = FALSE, echo = TRUE}
get_pattern_recognition(symbol = 'AAPL', 
                        resolution = 'D', 
                        api.key = api.key)
```
```{r, eval = TRUE, echo = FALSE}
get_pattern_recognition(symbol = 'AAPL', 
                        resolution = 'D', 
                        api.key = api.key) %>%
  head() %>%
  kable()
Sys.sleep(3)
```

### get_quote

`get_quote` retrieves real-time data for a given stock

#### Example

If we wanted a real-time quote for Apple, we'd enter

```{r, eval = FALSE, echo = TRUE}
get_quote(symbol = 'AAPL', 
          api.key = api.key)
```
```{r, eval = TRUE, echo = FALSE}
get_quote(symbol = 'AAPL', 
          api.key = api.key) %>%
  head() %>%
  kable()
Sys.sleep(3)
```

### get_stock_splits

`get_stock_splits` retrieves stock splits for a given symbol

#### Example

Let's say we want to get stock splits for Apple for a 10-year time period

```{r, eval = FALSE, echo = TRUE}
from.date = '2010-01-01'
to.date = '2020-01-01'

get_stock_splits(symbol = 'AAPL', 
                 from.date = from.date,
                 to.date = to.date,
                 api.key = api.key)
```
```{r, eval = TRUE, echo = FALSE}
from.date = '2010-01-01'
to.date = '2020-01-01'

get_stock_splits(symbol = 'AAPL', 
                 from.date = from.date,
                 to.date = to.date,
                 api.key = api.key) %>%
  head() %>%
  kable()
Sys.sleep(3)
```

Note: as-of 2020-07-14, this is not a very useful endpoint

### get_support_resistance

`get_support_resistance` retrieves support and resistance levels for a given company

#### Example

Let's say we want to get support and resistance levels for Apple with a resolution of 1 minute

```{r, eval = FALSE, echo = TRUE}
get_support_resistance(symbol = 'AAPL', 
                       resolution = 1,
                       api.key = api.key)
```
```{r, eval = TRUE, echo = FALSE}
get_support_resistance(symbol = 'AAPL', 
                       resolution = 1,
                       api.key = api.key) %>%
  head() %>%
  kable()
Sys.sleep(3)
```

### get_aggregate_indicators

`get_aggregate_indicators` retrieves aggregate signal of multiple technical indicators (e.g. MACD, RSI, MA)

#### Example

Let's say we want to get aggregate indicators for Apple with a resolution of 1 minute

```{r, eval = FALSE, echo = TRUE}
get_aggregate_indicators(symbol = 'AAPL', 
                       resolution = 1,
                       api.key = api.key)
```
```{r, eval = TRUE, echo = FALSE}
get_aggregate_indicators(symbol = 'AAPL', 
                       resolution = 1,
                       api.key = api.key) %>%
  head() %>%
  kable()
Sys.sleep(3)
```

### get_technical_indicators

`get_technical_indicators` retrieves technical indicator data for a given symbol

#### Example: indicator only

Let's say that we want to get the exponential moving average data for Apple over the past 5 hours with a resolution of 1 minute

```{r, eval = FALSE, echo = TRUE}
to.date <- Sys.time()
from.date <- to.date - (5*3600)

get_technical_indicators(symbol = 'AAPL', 
                         indicator = 'ema',
                         resolution = 1,
                         from.date = from.date, 
                         to.date = to.date, 
                         api.key = api.key)
```
```{r, eval = TRUE, echo = FALSE}
to.date <- Sys.time()
from.date <- to.date - (5*3600)

get_technical_indicators(symbol = 'AAPL', 
                         indicator = 'ema',
                         resolution = 1,
                         from.date = from.date, 
                         to.date = to.date, 
                         api.key = api.key) %>%
  head() %>%
  kable()
Sys.sleep(3)
```

#### Example: indicator plus parameters

We can also use a list of indicator parameters written by finnhub staff, found [here](https://docs.google.com/spreadsheets/d/1ylUvKHVYN2E87WdwIza8ROaCpd48ggEl1k5i5SgA29k/edit?usp=sharing). To get the triple exponential moving average (T3), we'd enter

```{r, eval = FALSE, echo = TRUE, message = FALSE, warning = FALSE}
to.date <- Sys.time()
from.date <- to.date - (5*3600)

indicator.list <- list(
  indicator = 't3',
  timeperiod = 3,
  seriestype = 'c'
)

get_technical_indicators(symbol = 'AAPL', 
                         indicator.list = indicator.list,
                         resolution = 1,
                         from.date = from.date, 
                         to.date = to.date, 
                         api.key = api.key)
```
```{r, eval = TRUE, echo = FALSE, message = FALSE, warning = FALSE}
to.date <- Sys.time()
from.date <- to.date - (5*3600)

indicator.list <- list(
  indicator = 't3',
  timeperiod = 3,
  seriestype = 'c'
)

get_technical_indicators(symbol = 'AAPL', 
                         indicator.list = indicator.list,
                         resolution = 1,
                         from.date = from.date, 
                         to.date = to.date, 
                         api.key = api.key) %>%
  head() %>%
  kable()
```