---
title: "finntools: finnhub.io made fast"
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
library(finntools)
```

# finntools

Finnhub.io offers a wide range of financial data at a price that the average investor can afford. However, much of this information is more useful to users in table format, rather than json. `finntools` helps shorten the gap between data retrieval and usage in a way that provides instant results for beginners and flexibility for more advanced users. Functions will be updated over time. Current ones retrieve:

* `get_company_news` news about a company within a given time period
* `get_sentiments` sentimental analyses of recent articles about a company
* `get_basic_financials` basic financial information about a company
* `get_reported_financials` financial information reported by a company through filings

## Installation
```{r, eval = FALSE}
### Install from Github
require(devtools)
devtools::install_github('atamalu/finntools')
```

## Functions

### get_company_news

`get_company_news` retrieves news about a company for a given time range

#### Parameters

##### required

`symbol` the stock symbol to retrieve company news for
`api.key` your API token from finnhub.io
`start.date`the earliest date to get news for (YYYY-MM-DD)
`end.date` the latest date to get news for (YYYY-MM-DD)
`last.n.days` the range of days to get data for
* ignore if using start.date and end.date

##### optional

`translate.date` declares whether UNIX time should be convered to YYYY-MM-DD date format
`write.file` declares whether data should be written to .csv file

#### Example

Let's say we want to get the last 30 days of news for Apple.

```{r, eval = FALSE}
get_company_news(symbol = 'AAPL', 
                 api.key = api.key,
                 last.n.days = 30)
```

Or we may want to get the last 30 days of news for Apple. Note: the API limits the number of results, which could be an issue for larger companies.

```{r, eval = FALSE}
get_company_news(symbol = 'AAPL', 
                 api.key = api.key,
                 start.date = '2020-03-01', 
                 end.date = '2020-03-30')
```

