---
title: "finntools: finnhub.io made fast"
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
library(finntools)
```

# finntools

Finnhub.io offers a wide range of financial data at a price that the average investor can afford. However, much of this information is more useful to users in table format, rather than json. `finntools` helps shorten the gap between data retrieval and usage in a way that provides instant results for beginners and flexibility for more advanced users. Functions will be updated over time. Current ones retrieve:

* `get_company_news` news about a company within a given time period
* `get_sentiments` sentimental analyses of recent articles about a company
* `get_basic_financials` basic financial information about a company
* `get_reported_financials` financial information reported by a company through filings

## Installation
```{r, eval = FALSE}
### Install from Github
require(devtools)
devtools::install_github('atamalu/finntools')
```

## Functions

### get_company_news

`get_company_news` retrieves news about a company for a given time range
<BR>
<BR>
<details>
  <summary>Parameters (expand)</summary>
`symbol` the stock symbol to retrieve company news for <BR>
`api.key` your API token from finnhub.io <BR>
`start.date`the earliest date to get news for (YYYY-MM-DD) <BR>
`end.date` the latest date to get news for (YYYY-MM-DD) <BR>
`last.n.days` the range of days to get data for <BR>
* ignore if using start.date and end.date <BR>
`translate.date` declares whether UNIX time should be convered to YYYY-MM-DD date format <BR>
`write.file` declares whether data should be written to .csv file
</details>

#### Example

Let's say we want to get the last 30 days of news for Apple.

```{r, eval = FALSE}
get_company_news(symbol = 'AAPL', 
                 api.key = api.key,
                 last.n.days = 30)
```

Or we may want to get the last 30 days of news for Apple. 

```{r, eval = FALSE}
get_company_news(symbol = 'AAPL', 
                 api.key = api.key,
                 start.date = '2020-03-01', 
                 end.date = '2020-03-30')
```

Note: the API limits the number of results, which could be an issue for larger companies.

### get_sentiments

`get_sentiments` retrieves sentiment analyses of recent articles for a given company
<BR>
<BR>
<details>
  <summary>Parameters (expand)</summary>
`symbol` the stock symbol to retrieve company news for <BR>
`api.key` your API token from finnhub.io <BR>
`write.file` declares whether data should be written to .csv file
</details>

#### Example

If we wanted to get sentiment analyses for Apple, we would use

```{r, eval = FALSE}
get_sentiments(symbol = "AAPL",
               api.key = api.key)
```

### get_basic_financials

`get_basic_financials` retrieves basic financial information for a given company
<BR>
<BR>
<details>
  <summary>Parameters (expand)</summary>
`symbol` the stock symbol to retrieve company news for <BR>
`api.key` your API token from finnhub.io <BR>
`metric.type` the type of metric to retrieve data for <BR>
* options include: "all", "price", "valuation", "margin" <BR>
`write.file` declares whether data should be written to .csv file
</details>

#### Example

To get basic financial price data for Apple, we would enter:

```{r, eval = FALSE}
get_basic_financials(symbol = "AAPL", 
                     api.key = api.key, 
                     metric.type = "price")
```

### get_reported_financials

`get_reported_financials` retrieves financial data through a company's filings
<BR>
<BR>
<details>
  <summary>Parameters (expand)</summary>
`symbol` the stock symbol to retrieve company news for <BR>
`api.key` your API token from finnhub.io <BR>
`frequency` the time period encompassed by the report(s) <BR>
* options include: "annual", "quarterly" <BR>
`write.file` declares whether data should be written to .csv file
</details>

#### Example

To get annual reported financial data for Apple, we would enter:

```{r, eval = FALSE}
get_reported_financials(symbol = "AAPL", 
                     api.key = api.key, 
                     frequency = "annual")
```